Bucket-Sorted Independent Sets for Algebraic Multigrid

### 2007-09-19 bsis_paper/paper.tex
A few edits. Still some reorganization to do.
git-svn-id: file:///home/rblake/svn/pamg/trunk@26 c7f3fe13-8c30-0410-9127-9a9c42fe009c

\subsection{CLJP-c}
Recall that CLJP-c colors the graph of $S$ before selecting
$C$-points, and the colors are used as one component of the vertex
weights. As a result, the structure of the coarse grids selected is
improved. More formally, the use of graph coloring provides the
following important result.
\begin{thm}
\label{5:theorem:CLJPc-neighbor-independence}
For all pairs of vertices $i$ and $j \in \mathcal{N}_i$ CLJP-c
guarantees $w_i \ne w_j$.
\end{thm}
\begin{proof}
Assume two adjacent vertices $i$ and $j$ have the same weight. That is,
$|S_i^T| = |S_j^T|$ and the weight augmentation provided through
coloring is the same for $i$ and $j$. The graph of $S$, however, is
colored such that $i$ and $j$ are different colors for all $j \in
\mathcal{N}_i$, so a contradiction is reached.
\end{proof}
Theorem~\ref{5:theorem:CLJPc-neighbor-independence} establishes that
all adjacent vertices have different weights in CLJP-c, which is not
guaranteed in CLJP, although is unlikely to occur. The following
corollaries are a result of
Theorem~\ref{5:theorem:CLJPc-neighbor-independence}.
\begin{cor}
Any set of vertices in the graph of $S$ that share the same weight is
an independent set.
\end{cor}
\begin{cor}
\label{5:cor:max-weight-indep-set}
The set of vertices with the largest weight in the graph of $S$ form
an independent set satisfying~\ref{5:eqn:D-conditions}. That is, each
vertex in that independent set has a uniquely maximal weight in its
neighborhood.
\end{cor}
The first corollary states that independent sets can be selected in
the graph simply by selecting sets of vertices with the same
weight. Corollary~\ref{5:cor:max-weight-indep-set} refines this
observation to a subset of vertices guaranteed to satisfy the
selection criterion. In particular, it shows it is possible to build
the coarse grid by selecting vertices with the maximum weight,
updating weights, selecting the next set of vertices with maximum
weight, and so on. This approach is taken by the algorithm developed
in Section~\ref{5:sec:contribution}. It is proven in
Section~\ref{5:sec:cg-invariance} that despite the difference in
approach, the resulting coarse grid is the same as that selected by
CLJP-c.

\subsection{BSIS}
\label{sec:bsis}
In this section, new techniques for searching the graph of $S$ for new
$C$-points and subsequently updating the weights of remaining vertices
are developed. The new algorithm is labeled Bucket Sorted Independent
Sets (BSIS) to reflect the data structure used.

>>>>

\subsection{CLJP-c}
CLJP-c~\cite{alber-cljpc} colors the graph of $S$ before selecting
$C$-points, and the colors are used as one component of the vertex
weights. As a result, the structure of the coarse grids selected is
improved. More formally, the use of graph coloring provides the
following important result.
\begin{thm}
\label{5:theorem:CLJPc-neighbor-independence}
For all pairs of vertices $i$ and $j \in \mathcal{N}_i$ CLJP-c
guarantees $w_i \ne w_j$.
\end{thm}
\begin{proof}
Assume two adjacent vertices $i$ and $j$ have the same weight. That is,
$|S_i^T| = |S_j^T|$ and the weight augmentation provided through
coloring is the same for $i$ and $j$. The graph of $S$, however, is
colored such that $i$ and $j$ are different colors for all $j \in
\mathcal{N}_i$, so a contradiction is reached.
\end{proof}
Theorem~\ref{5:theorem:CLJPc-neighbor-independence} establishes that
all adjacent vertices have different weights in CLJP-c, which is not
guaranteed in CLJP, although is unlikely to occur. The following
corollaries are a result of
Theorem~\ref{5:theorem:CLJPc-neighbor-independence}.
\begin{cor}
\label{cor:same-weight-indep-set}
Any set of vertices in the graph of $S$ sharing the same weight are an
independent set.
\end{cor}
\begin{cor}
\label{cor:max-weight-indep-set}
The set of vertices with the largest weight in the graph of $S$ form
an independent set satisfying~\ref{5:eqn:D-conditions}. That is, each
vertex in that independent set has a uniquely maximal weight in its
neighborhood.
\end{cor}
Corollary~\ref{cor:same-weight-indep-set} states that independent sets
can be selected in the graph simply by selecting sets of vertices with
the same weight. Corollary~\ref{cor:max-weight-indep-set} refines this
observation to a subset of vertices guaranteed to satisfy the
selection criterion. In particular, it shows it is possible to build
the coarse grid by selecting vertices with the maximum weight,
updating weights, selecting the next set of vertices with maximum
weight, and so on. This approach is taken by the algorithm developed
in Section~\ref{5:sec:contribution}. It is proven in
Section~\ref{5:sec:cg-invariance} that despite the difference in
approach, the resulting coarse grid is the same as that selected by
CLJP-c.

\subsection{BSIS}
\label{sec:bsis}
In this section, new techniques for searching the graph of $S$ for new
$C$-points and subsequently updating the weights of remaining vertices
are developed. The new algorithm is named Bucket Sorted Independent
Sets (BSIS) to reflect the data structure used.
